opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-07-05 chapters/04_our_dataset.tex
Commited external author contribution
Test commit
Commited INT contribution paragraph

%% Paragraph by FX Coudert and Arthur Hardiagon
%% !! work in progress !!

@@

The pXRD data from the COD database are of high quality, with a median resolution of $\Delta(2\theta) = 0.013$\textdegree and an average number of 9190 points measured per pattern.

% todo : short analysis of the data

@@

>>>>

%% Paragraph by FX Coudert and Arthur Hardiagon
%% Chimie Paris Tech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France

@@

The pXRD data from the COD database are of high quality, with a median resolution of $\Delta(2\theta) = 0.013$\textdegree and an average number of 9190 points measured per pattern. They span a wide chemical space, including organic, inorganic and hybrid structures, including 75 different elements of the periodic table.

@@

%% Institute of Theoretical Informatics, Karlsruhe Institute of Technology,
%Kaiserstr. 12, 76131 Karlsruhe, Germany

The X-ray diffraction data were collected on a Bruker D8 Advance (Cu Kα1 radiation, λ = 1.54056 Å). The samples were initially recorded for various research projects over the last ten years and were measured with different step sizes, times per step, and over different angle ranges, but all using Cu Kα1 radiation. The samples mostly contained transition metal oxides, sulfides, and fluorides. A major part of the research focused on high-entropy materials, which involved incorporating many different elements into single-phase structures, leading to peak shifts or phase separations. Most of those multicomponent complex materials appeared in various structures, including rock-salt, spinel, fluorite, perovskite, and delafossite, to name a few.The samples were almost always prepared in powder form; therefore, powder XRD was performed on samples with adjusted height. To improve statistics, the samples were rotated during the entire measurement. Some air-sensitive samples were measured using a transparent polymer dome for protection. This dome led to increased background noise over the first 20° and slightly decreased pattern resolution. The samples were prepared using various synthesis techniques, mostly solid-state or wet chemical syntheses, to obtain the desired structures. Consequently, particle size and crystallinity varied significantly. The sample set also includes samples that were not successfully measured or where phases could not be identified.
